Air cargo load and route planning in pickup and delivery operations

### 2024-01-28 latex/responses.tex
GA DEAP for ACLPP not working

	\citep{PeerlinckAmy2022MFEO} applied DEAP to solve a multi-objective knapsack problem. We adapted their algorithm to solve the ACLPP in each node of this work's solution.

Our algorithm is not complete, as we did not include the constraints regarding the weight and balance problem or the pickup and delivery problem.

In the first attempt, considering only the weight and volume constraints, our implementation of DEAP managed to solve problems up to 100 items to be allocated to 18 pallets in less than 10 seconds.

When we included the item count constraint to prevent each item from being allocated to more than one pallet, it was able to solve only small problems (20 items on 2 pallets).

@@

For the crossover probability, we tested the range [0.6 ? 0.8], and for the mutation probability, we tested from 0.01 to 0.1 with no success.

Up to this point in time, we had no success solving the ACLPP with DEAP.

@@

		}
	\end{minipage}
\end{center}

@@

	\begin{figure}[H]
		\centering
		\caption{\label{fig:brazil} {\it Shims/GA} best tour (may not be optimal)}
		\includegraphics[scale=0.3]{brazil.png}
	\end{figure}

>>>>

	\citep{PeerlinckAmy2022MFEO} applied DEAP to solve a multi-objective knapsack problem.

	Our GA implementation is not complete. Due to performance issues, we did not include the constraints regarding the Weight and Balance Problem or the Pickup and Delivery Problem.

	In the first attempt, considering only the weight and volume constraints, our implementation of DEAP managed to solve problems up to 100 items to be allocated to 18 pallets in less than 10 seconds.	
	When we included the item count constraint to prevent each item from being allocated to more than one pallet, it was able to solve only small problems (20 items on 2 pallets).

@@

	For the crossover probability, we tested the range [0.6 - 0.8], and for the mutation probability, we tested from 0.01 to 0.1 with no success.

@@

Large chromosome sizes, like 18,000-dimension arrays, can pose significant challenges in using Genetic Algorithms (GA).

The computational complexity is significant, as each generation requires evaluating individual fitness, which can be resource-intensive.

Large chromosomes can slow GA convergence due to the vast search space, potentially requiring more generations to find optimal solutions.

Efficient encoding and decoding of the problem into the chromosome and decoding solutions is crucial for a 18,000-dimension array. 
Also, the design of the fitness function becomes more critical as chromosome size increases, as it needs to guide the evolutionary process without being overly computationally demanding.

Up to this point in time, we had no success solving the ACLPP with DEAP because it included the palletization planning of 200 to 1000 items per node in a set of 18 aircraft pallets.
		}
	\end{minipage}
\end{center}

@@

	\begin{figure}[H]
		\centering
		\caption{\label{fig:brazil} {\it Shims/GA} best ACLP+RPDP tour}
		\includegraphics[scale=0.3]{brazil.png}
	\end{figure}
